Sagan Ipsum and a Workflow Guide with Make, R, R Markdown, and Some {stevetemplates}

### 2021-03-22 inst/skeleton/ms.Rmd
new output drop

if (is_latex) {
  conditional_dpi <- 96
  return(conditional_dpi)
} else if (is_docx) {
  conditional_dpi <- 600
  return(conditional_dpi)
} else {}

@@

\vspace{.5cm}
\begin{hypothesis}
\begin{minipage}[t]{5.1 in}
This is a hypothesis, but only for LaTeX. MS Word will pass over it like a good boy. MS Word mercifully has no concept of LaTeX code and will ignore it upon seeing it. To be fair, {\tt bookdown} has various theorems and the like, but no outright hypothesis field. This will have to do.
\end{minipage}
\end{hypothesis}
\vspace{.5cm}

```{r h1, eval=is_docx, results="asis"}
cat('> **H1**: This is a hypothesis, but only for MS Word. Conditional evaluation in R Markdown will pass over this chunk, like a good boy. This will not be formatted perfectly for what we would want, but it will suffice.') 
```

>>>>

if (is_latex) {
  conditional_dpi <- 96
  return(conditional_dpi)
} else {
  conditional_dpi <- 600
  return(conditional_dpi)
}

@@

\vspace{.5cm}
\begin{hypothesis}
\begin{minipage}[t]{5.1 in}
This is a hypothesis, but only for LaTeX. MS Word will pass over it like a good boy, as will HTML. Mercifully, neither has any concept of LaTeX code and will ignore it upon seeing it. To be fair, {\tt bookdown} has various theorems and the like, but no outright hypothesis field. This will have to do.
\end{minipage}
\end{hypothesis}
\vspace{.5cm}

```{r h1, eval=!is_latex, results="asis"}
cat('> **H1**: This is a hypothesis, but not for LaTeX. Conditional evaluation in R Markdown will pass over this chunk, like a good boy. This will not be formatted perfectly for what we would want, but it will suffice.') 
```
